Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Wording

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertions} in
    traditional unit testing frameworks, but use a different
    terminology.

@@

The \texttt{describe} function combines a list of specs into a larger spec.
% It can be used to organize a spec as a tree.
% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested, and a report is generated.
Behavior with evidence that does not hold is marked in the generated
report as {\tt FAILED}.

>>>>

\item[expectation]
    Expectations are used to express the expected outcome of a code
    example.  They serve the same purpose as \emph{assertions} in
    traditional unit testing frameworks, but use a different
    terminology.

@@

The \texttt{describe} function combines a list of specs into a larger spec.
% It can be used to organize a spec as a tree.
% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested, and a report is generated.  Behavior with
evidence that does not hold is marked as {\tt FAILED} in the generated
report.
